The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-04-07 SC-challenge.tex
more small changes

Finally on the topic of peer review of software, the authors note that there is a distinct lack of standardization around the practices of peer review. Journals  accepting `software' submissions (e.g., F1000Research, SoftwareX and JORS) often conflate the review of the submitted software with a review of research output produced \textit{by} the software. One exception to this is the rOpenSci community who recently published their review process~\cite{rOpenSci-reviews} used to determine whether a package can become part of the rOpenSci project.
\asnote{This language might be too strong}

>>>>

Finally on the topic of peer review of software, we note that there is a distinct lack of standardization around the practices of peer review. Journals  accepting `software' submissions (e.g., F1000Research, SoftwareX, and JORS) often conflate the review of the submitted software with a review of research output produced \textit{by} the software. One exception to this is the rOpenSci community, who recently published the review process~\cite{rOpenSci-reviews} they use to determine whether a package can become part of the rOpenSci project.
\asnote{This language might be too strong} \katznote{seems ok to me}
